Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2014-07-31 paper.tex
Minor updates.

\subsection{Initial Models}

@@

@@

>>>>

\subsection{Initial Models}
\label{sec:initial_models}

@@

In this section we describe a series of test problems that couple the hydrodynamics, gravity, and EOS modules.

@@

In Section \ref{sec:initial_models} we describe the process by which we generate initial stellar models. While the 1D models are in hydrostatic equilibrium to within a small error, interpolation onto the 3D Cartesian grid will introduce perturbations into the solution \citep{zingale:2002}. Although we ensure that the initial models are generated with the same equation of state and are as well resolved as our finest grid, there will still be a hydrodynamical error associated with the fact that the rectangular grid cannot faithfully represent a spherical star. Additionally, the gravitational potential obtained by the multigrid solver will differ slightly from the one assumed by the initial model, and the operator splitting between the gravity and hydrodynamics should also result in small errors. As a result, we expect that the star will oscillate slightly about an equilibrium point, but that the amplitude of this oscillation should decrease with increasing resolution.
